Exploring Red Wine Quality by Jin Lim
========================================================

> The Red Wine dataset concerns the red variant of the Portuguese "Vinho Verde" 
wine. It contains 1599 observations and 11 input variables, as well as an output
variable called "quality" on a scale of 0 (very bad)-10 (very excellent). Our 
task is to determine which variables have statistically significant impacts on 
the quality of wine. 

> This dataset is provided by Udacity and is named "wineQualityReds.csv"

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(dplyr)
library(GGally)
library(gridExtra)
library(scales)
library(memisc)
```
# Structure and Summary of Dataframe

```{r echo=FALSE, message=FALSE, Load_and_Prepare_the_Data}
# Load the Data
red <- read.csv('C:/Users/--/Desktop/wineQualityReds.csv')
# Remove "X" variable as it is not described in the overview, and appears to 
# simply be a unique identifier
red$X <- NULL
# Overview of the dataframe
names(red)
summary(red)
str(red)
```

# Univariate Plots Section

```{r echo=FALSE, Univariate_Plots}
ggplot(data = red, aes(x = quality)) +
  geom_bar(width = 1, color = 'black',fill = I('blue'))
```

> Let's look at quality first. From the plot, it appears that most wines are 
of average (5-6) quality. This is consistent with my expectations as most 
wine-tasters will usually not grade in extremes as a part of human nature. That
is, they will "average" the results in their head and save extreme scores for 
extreme wines. 

```{r}
grid.arrange(ggplot(red, aes(x = fixed.acidity)) + 
               geom_histogram(binwidth = 1, color = 'black', fill= 'pink'),
ggplot(red, aes(x = volatile.acidity)) +
  geom_histogram(binwidth = 0.05, color = 'black', fill = I('red')))
```

> For acidity, Fixed Acidity seems to be fairly normally-distributed, with a 
positive or right skew. Volatile Acidity seems to be bimodal, with peaks at 0.4 
and 0.6. 

```{r}
grid.arrange(ggplot(data = red, aes(x = citric.acid)) +
               geom_histogram(binwidth = 0.08, color = 'black', 
                              fill = I('orange')) +
               scale_x_continuous(breaks = seq(0,1,0.1), lim = c(0,1)),
ggplot(data = red, aes(x = citric.acid)) +
  geom_histogram(binwidth = 0.08, color = 'black',fill = I('orange')) +
  scale_x_log10(breaks = seq(0, 1.2, 0.1)))
```

> We scale Citric Acid by log10 due to its long right-tail. Interestingly, the transformation now yields a long left-tail. This could be further explored in the bivariate analysis section. 

```{r}
ggplot(data = red, aes(x = residual.sugar)) +
  geom_histogram(binwidth = 0.1, color = 'black',fill = I('orange')) +
  scale_x_continuous(lim = c(1,8))
```

> Residual sugar is very positively skewed and has peaks around 2. It has a lot
of outliers on the right-tail. 

```{r}
ggplot(data = red, aes(x = chlorides)) +
  geom_histogram(binwidth = 0.01, color = 'black',fill = I('orange')) +
  scale_x_continuous(lim = c(0,0.25))
```

> Chlorides has a similar distribution to Residual Sugar. We see a strong 
concentration of points around the median and extreme outliers. 

```{r}
grid.arrange(ggplot(data = red, aes(x = free.sulfur.dioxide)) +
               geom_histogram(binwidth = 1, color = 'black', 
                              fill = I('orange')) +
               scale_x_continuous(breaks = seq(0,80,5), lim = c(0,45)),
ggplot(data = red, aes(x = total.sulfur.dioxide)) +
  geom_histogram(binwidth = 5, color = 'black',fill = I('orange')) +
  scale_x_continuous(lim = c(0,180)))
```

> Relative to the other plots, Free Sulfur Dioxide has a relatively dispersed
distribution, but again it has extreme outliers on its right-tail. Total Sulfur
Dioxide is less-dispersed, but still follows the same pattern. 

```{r}
grid.arrange(ggplot(data = red, aes(x = density)) +
               geom_histogram(binwidth = 0.001, color = 'black', 
                              fill = I('dark grey')), 
ggplot(data = red, aes(x = pH)) +
  geom_histogram(binwidth = 0.1, color = 'black',fill = I('purple')))
```

> Both Density and pH are very normally distributed, with concentrations around
0.995-1 and 3.2-3.5 respectively. 

```{r}
ggplot(data = red, aes(x = sulphates)) +
  geom_histogram(binwidth = 0.1, color = 'black',fill = I('orange')) +
  scale_x_continuous(lim = c(0.3,1.8))
```

> At first glance, Sulphates is certainly more positively skewed than Density 
and PH, but I would say the data is still fairly normally-distributed around 
0.6. It does not have as many extreme outliers as Chlorides and 
Free/Total Sulphur Dioxide. 

```{r}
ggplot(data = red, aes(x = alcohol)) +
  geom_histogram(binwidth = 0.1, color = 'black',fill = I('orange')) +
  scale_x_continuous(lim = c(8,14))
```

> Alcohol is right-skewed, though not to the extent of Chlorides and Free/Total
Sulphur Dioxide. 

# Univariate Analysis

### What is the structure of your dataset?

> There are 1599 observations of red wine with twelve features and a (removed)
unique identifier. All values are numerical save for quality, which is an 
integer. 

### What is/are the main feature(s) of interest in your dataset?

> The main feature of interest is the output variable "quality". 

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

> I would expect alcohol and residual sugar to be fairly positively-correlated
with quality. On the other hand, the more extreme the value of pH, the less
quality should result. 

### Did you create any new variables from existing variables in the dataset?

> No, I did not. I could have perhaps combined fixed/volatile acidity into 
something like "total acidity", but I do not think that would affect the quality
very much by itself. 

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

> 1. Citric Acid has a large number of 0 values. I wonder how it can be that 
some wines do not have this value if most are made of similar grapes. Also, 
scaling Citric Acid by log10 reverses the tail.  
2. I was also surprised by the number of extreme outliers in many of the 
variables. If most of the wines have an average rating, this could mean that
for some features, going in an extreme direction does not actually have a
signficant impact on taste, if at all. 
3. For several plots, I did my best to limit the most extreme outliers via 
scaling limits.

# Bivariate Plots Section

```{r echo=FALSE, Bivariate_Plots}
ggcorr(red, label=TRUE)
ggpairs(red)
```

> The top 4 factors correlated with wine quality (>0.2) are: alcohol (0.476), 
volatile acidity (-0.391), sulphates (0.251), and finally citric acid (0.226). 

```{r}
#Let's convert quality from an integer to a factor variable so that 
# box plots can be used
red$quality <- factor(red$quality)

ggplot(red, 
       aes(x=quality, y=alcohol,fill=quality)) + 
       geom_boxplot()+
       xlab("Quality") + ylab("Alcohol") +
       ggtitle("Alchohol and Quality")
```

> We converted quality from an integer to a factor in order to plot with box 
plots. At least one of our assumptions was right: the higher the alcohol content 
of the wine, the higher the wine is rated. 

```{r}
ggplot(red, 
       aes(x=quality, y=residual.sugar,fill=quality)) + 
       geom_boxplot()+
       xlab("Quality") + ylab("Residual Sugar") +
       ggtitle("Residual Sugar and Quality")
```

> My assumption about residual sugar was wrong. This is the sugar left after
fermentation, so perhaps wine-tasters put more stock by other flavors than 
sweetness. 

```{r}
ggplot(red, 
       aes(x=quality, y=volatile.acidity,fill=quality)) + 
       geom_boxplot()+
       xlab("Quality") + ylab("Volatile Acidity") +
       ggtitle("Volatile Acidity and Quality")
```

> The more volatile acids there are in a wine, the lower it is rated. Our 
assumption was based on pH, in that extreme values will have lower scores. Let
us examine that next. 

```{r}
ggplot(red, 
       aes(x=quality, y=pH,fill=quality)) + 
       geom_boxplot()+
       xlab("Quality") + ylab("pH") +
       ggtitle("pH and Quality")
```

> And oddly enough, it would appear that lesser pH (more acidity) has a 
correlation with higher quality. So now we have an interesting relationship on
our hands: volatile acidity is negatively correlated with quality, but recall
citric acid is positively correlated (0.226). It would be worth examining all 
the acidic factors on a log scale against pH to understand how each factor works 
in determining acidity. 

```{r}
ggplot(data = red, aes(x = fixed.acidity, y = pH)) +
  geom_point(alpha = 0.4) +
  scale_x_log10(breaks=seq(5,15,1)) +
  xlab("Fixed Acidity Log10") +
  geom_smooth(method="lm")

ggplot(data = red, aes(x = volatile.acidity, y = pH)) +
  geom_point(alpha = 0.4) +
  scale_x_log10(breaks=seq(5,15,1)) +
  xlab("Volatile Acidity Log10") +
  geom_smooth(method="lm")

ggplot(data = red, aes(x = citric.acid, y = pH)) +
  geom_point(alpha = 0.4) +
  scale_x_log10(breaks=seq(5,15,1)) +
  xlab("Citric Acid Log10") +
  geom_smooth(method="lm")
```

> Fixed and Citric acids correlate with pH as we expected; that is to say, the 
more acids, the lower the pH value. 

> Volatile acidity is odd. The overview suggests it is acetic acid, and that 
high concentrations impart a vinegar taste. It is, however, positively 
correlated with pH, and yet we know lower pH means more acidity. This should 
mean more volatile acidity -> lower pH. Perhaps the more acid is present as 
"volatile" instead of fixed, the more it evaporates, thus leaving a less acidic 
pH (assuming wine-tasters wait before drinking).

```{r}
ggplot(data=red, aes(x=quality, y=sulphates)) +
  geom_jitter( alpha = .3) +
  geom_boxplot(alpha = .5,color = 'black') +
  scale_y_continuous(lim=c(.25,1)) +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)

ggplot(data=red, aes(x=quality, y=sulphates)) +
  geom_jitter( alpha = .3) +
  geom_boxplot(alpha = .5,color = 'black') +
  ylab('sulphates log10') +
  scale_y_log10(lim=c(.25,1), breaks=c(0.25,0.5,0.75,1)) +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

> And here we have the sulphates and sulphateslog10 plots. The more sulphates
are present in a wine, the higher its quality. This is consistent as sulphates
act as antimicrobials and antioxidants, and thus help preserve a wine. We also
decided to scale the plot due to the factor's original right skew. 

```{r}
ggplot(data=red, aes(x=quality, y=citric.acid)) +
  geom_jitter( alpha = .3) +
  geom_boxplot(alpha = .5,color = 'blue') +
  scale_y_continuous(lim=c(.1,1)) +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)

ggplot(data=red, aes(x=quality, y=citric.acid)) +
  geom_jitter( alpha = .3) +
  geom_boxplot(alpha = .5,color = 'blue') +
  ylab('citric acid log10') +
  scale_y_log10(lim=c(.1,1), breaks=c(0.25, 0.5, 0.75,1)) +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

> Finally, citric acid and quality. Recall we reversed the skew of citric acid 
when we plotted it in log10. Here are both graphs, and it can be seen that 
higher citric acid values result in a higher quality. There are outliers where
crossing a certain threshold results in drastically lowered quality, but the
general rule still stands. 


```{r}
ggplot(red, 
       aes(x=quality, y=density,fill=quality)) + 
       geom_boxplot()+
       xlab("Quality") + ylab("Density") +
       ggtitle("Density and Quality")

ggplot(red, 
       aes(x=quality, y=total.sulfur.dioxide,fill=quality)) + 
       geom_boxplot()+
       xlab("Quality") + ylab("Total Sulfur Dioxide") +
       ggtitle("Total Sulfur Dioxide and Quality")
```

> And just to be thorough, here are the plots for two other factors that had 
correlations close to 0.2: density (-0.175) and total sulfur dioxide (-0.185). 

> Density can be explained, I think. Alcohol is lighter than water, and we 
already know alcohol was one of our strongest correlative variables; thus, the
more alcohol, the less density and the higher the quality. It could also 
contribute to an "airy" feeling. We'll test that in the next plot.

> Total sulfur dioxide is also consistent in that more of it can affect the 
taste of the wine, though the box plot suggests this is an inconsistent 
correlation at best.

```{r}
ggplot(data=red, aes(x=alcohol, y=density)) +
  geom_jitter(alpha=0.3) +
  geom_smooth(method='lm')
```

> Here we see that more alcohol results in less density, so density is more a
function of that than a predictor of quality. 

```{r}
#Let's try a simple linear regression model on our strongest correlative 
# variable, alcohol.
alcohollm <- lm(as.numeric(quality) ~ alcohol,
                       data = red)
summary(alcohollm)
```

> A simple linear regression model of alcohol returns an R-squared of about
0.23. Despite its low value, I am quite pleased with the result. I did not 
expect one factor to be able to fully explain quality when there are so many 
other variables at play. Alcohol will be an important piece of the puzzle. 

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

> 1. Alcohol (positive), volatile acidity (negative), sulphates (positive) and
citric acid (positive) are the strongest predictors of wine quality. 
2. Surprisingly, residual sugar had almost no explanatory effect on wine 
quality. 
3. Despite volatile acidity's negative effect on quality, as a general rule, the
more acidic the wine, the better it tastes. 

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

> 1. The most surprising relationship was volatile acidity's positive 
correlation with pH. We'd assume more acids result in more acidity (i.e, lower
pH), especially when fixed acidity and citric acid both exihibit the expected
trend on pH. 
2. Also of note is fixed acidity's strong (0.668) positive correlation with 
density. I am unsure how this relationship works. 

### What was the strongest relationship you found?

> The strongest relationship on quality was alcohol. The strongest relationships
overall were fixed acidity -> pH (negative), citric acid (positive) at around 
0.7. 

# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}
ggplot(data = red, aes(y = density, x = alcohol, color = quality)) +
  geom_jitter(alpha = 0.5, size = 3) +
  scale_colour_manual(values=c('red', 'orangered1', 'indian red', 'cyan', 
                               'purple', 'blue')) +
  xlab("Alcohol") +
  ylab("Density")
```

> As can be seen from the plot, higher quality wines in blue colors tend to have
high alcohol content and low densities. Holding alcohol constant, density has
no real explanatory effect on wine quality, confirming our prior guess that it
was alcohol contributing to lower density and its slight positive correlation 
with quality. 

```{r}
ggplot(red, aes(y=volatile.acidity,x=alcohol,color = quality)) +
  geom_jitter(alpha=0.5, size=3) +
  xlab("Alcohol") + 
  ylab("Volatile Acidity") +
  scale_colour_manual(values=c('red', 'orangered1', 'indian red', 'cyan', 
                               'purple', 'blue'))
```

> The highest quality wines tend to have low volatile acidity and high alcohol
content. 

```{r}
ggplot(data = red, aes(y = sulphates, x = alcohol, color = quality)) +
  geom_jitter(alpha = 0.5, size = 3) +
  scale_colour_manual(values=c('red', 'orangered1', 'indian red', 'cyan', 
                               'purple', 'blue')) +
  xlab("Alcohol") +
  ylab("Sulphates")
```

> For sulphates, generally higher quality wines tend to have higher levels of 
alcohol and sulphates. Let's put these three variables which had the highest 
correlation with quality (alcohol, volatile acidity, sulphates) together. 

```{r}
#Let's add the log10 of sulphates to the list and use it to plot
red <- mutate(red, logsulphates = log10(sulphates))

ggplot(red, aes(x=alcohol,y=volatile.acidity)) +
  geom_jitter(aes(color = logsulphates, alpha= 1/2, size= 1/2))+
  xlab("Alcohol") + 
  ylab("Volatile Acidity") +
  scale_colour_gradient2(low="red", high="blue", 
                         mid="purple", midpoint= -0.1) +
  facet_grid(quality ~ .) 
```

> We've changed the color coding for this plot. Now, the log10 of sulphates 
ranges from red (low sulphates) to blue (high sulphates), and the graph is 
faceted over quality with volatile acidity on the y-axis and alcohol on the 
x-axis. As a general rule, higher-quality wines have more alcohol (concentrated
right), less volatile acidity (concentrated low), and more sulphates (more blue
than red). 

> We scaled sulphates by log10 in order to normalize its right tail. 

```{r}
ggplot(red, aes(x=citric.acid,y=volatile.acidity)) +
  geom_jitter(aes(color = logsulphates, alpha= 1/2, size= 1/2))+
  xlab("Citric Acid") + 
  ylab("Volatile Acidity") +
  scale_colour_gradient2(low="red", high="blue", 
                         mid="purple", midpoint= -0.1) +
  facet_grid(quality ~ .) 
```

> Finally, we look at citric acid using the same format. This one is not as 
clear as when alcohol was the x-axis, but again, you can see a general pattern 
where higher quality wines have more sulphates, less volatile acidity and 
slightly more right-skew. 

#### Now we will generate a linear model for the strongest predictors of \ 
wine quality (with values at or close to 0.2): alcohol, sulphates, \ 
volatile acidity, citric acid, chlorides, total sulfur dioxide and density \

```{r}
m1 <- lm(as.numeric(quality) ~ alcohol, data=red)
m2 <- update(m1, ~. + sulphates)
m3 <- update(m2, ~. + volatile.acidity)
m4 <- update(m3, ~. + citric.acid)
m5 <- update(m4, ~. + chlorides)
m6 <- update(m5, ~. + total.sulfur.dioxide)
m7 <- update(m6, ~. + density)
mtable(m1, m2, m3, m4, m5, m6, m7)
```

> This model is described as: quality = 0.985 + 0.276alcohol + 0.908sulphates
- 1.104volatile.acidity + 0.065citric.acid - 1.763chlorides 
- 0.002total.sulphur.dioxide 

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

> 1. Citric acid has a small but noticeable effect on the quality of wine. 
2. As a general rule, more sulphates and alcohol are the strongest predictors
of a high rating.
3. More volatile acidity is the strongest predictor of a lower rating. 

### Were there any interesting or surprising interactions between features?

> At this point, after so much exploration of the data, most of the interactions
uncovered were expected.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

> I created a multiple linear regression model. At the end of the day, 
R-squared tops out at around 0.352, so still a fairly low number; but again, I
am relatively pleased with the result as we are working with data that has 
human biases. 

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(data=red, aes(y=alcohol, x=quality)) + 
  geom_jitter(alpha = .3)  +
  geom_boxplot(alpha = .5,color = 'black') +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4) +
  xlab("Quality") +
  ylab("Alcohol") +
  ggtitle("Effect of Alcohol on Wine Rating")
```

### Description One

> Our strongest relationship and the best predictor of wine rating. The higher
the alcohol content of a wine, the better the tasters rated it. Looking at the
plot, means and medians tend to coincide for each facet of quality, and thus
for a particular "quality grade", the distribution is fairly normal. 

### Plot Two
```{r echo=FALSE, Plot_Two}
p1 <-
ggplot(red, aes(x=quality, y=volatile.acidity,fill=quality)) +
      geom_boxplot()+
      xlab("Wine Rating") + 
      ylab("Volatile Acidity") +
      ggtitle("Effect of Volatile Acidity on Wine Rating")

p2 <-
ggplot(red, aes(x=quality, y=sulphates,fill=quality)) +
      geom_boxplot()+
      xlab("Wine Rating") + 
      ylab("Sulphates") +
      ggtitle("Effect of Sulphates on Wine Rating")

p3 <-
ggplot(red, aes(x=quality, y=citric.acid,fill=quality)) +
      geom_boxplot()+
      xlab("Wine Rating") + 
      ylab("Citric Acid") +
      ggtitle("Effect of Citric Acid on Wine Rating")
      grid.arrange(p1, p2, p3)
```

### Description Two

> And the next three strongest predictors. Volatile acidity (acetic acid) has a 
consistent downward effect on wine rating. Sulphates (antimicrobial and 
antioxidant additives) have a consistent upward effect on wine rating. Citric
acid (affects "freshness" of wine) has a small but noticeably positive effect on
rating. These three work with alcohol to produce the best-rated wines.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(red, aes(y=volatile.acidity,x=alcohol,color = quality)) +
  geom_jitter(alpha=0.5, size=3) +
  xlab("Alcohol") + 
  ylab("Volatile Acidity") +
  scale_colour_manual(values=c('red', 'orangered1', 'indian red', 'cyan', 
                               'purple', 'blue')) +
  ggtitle("Alcohol, Volatile Acidity, and Quality")

ggplot(red, aes(y=citric.acid,x=logsulphates,color = quality)) +
  geom_jitter(alpha=0.5, size=3) +
  xlab("Sulphates Log10") + 
  ylab("Citric Acid") +
  scale_colour_manual(values=c('red', 'orangered1', 'indian red', 'cyan', 
                               'purple', 'blue')) +
  ggtitle("Sulphates, Citric Acid, and Quality")
```

### Description Three

> And so, putting all four factors (Alcohol, Volatile Acidity, Sulphates and 
Citric Acid together) together. The best-rated wines tend to have a high alcohol 
content and low volatile acidity. They also tend to have more citric acid and 
sulphates. 

------

# Reflection

> The Red Wine dataset concerns the red variant of the Portuguese "Vinho Verde" 
wine. It contains 1599 observations and 11 input variables, as well as an output variable called "quality" on a scale of 0 (very bad)-10 (very excellent). There
is no single fully-robust explanatory relationship between these variables and
quality; rather, the inputs all work together to guide wine rating. The four 
variables with the most driving force are alcohol (0.476), volatile 
acidity (-0.391), sulphates (0.251) and citric acid (0.226). These variables 
were the main point of focus in most of this project's visualizations. 

> Observations and reflections on variables:  
1. **Alcohol:** Alcohol is the most correlated factor with wine quality. The
higher the alcohol rating, the better the tasters rated the wine. Perhaps the
alcohol content itself imparts a sharper and stronger taste. More likely, 
alcohol content is a result of fermentation length; the longer the fermentation,
the more alcohol extracted, and the greater the perception of "quality" and 
perhaps subtle tastes imparted by aging.   
2. **Volatile Acidity:** Or acetic acid. The more acetic acid, the lower the 
wine is rated. Obviously, a vinegar-like taste cannot be good for ratings.   
3. **Sulphates:** These are added to wines in order to combat bacterial growth
and prevent spoilage. It would make sense that wines with the least spoilage
taste the best.   
4. **Citric Acid:** Another additive to wines. The large number of "0" citric
acid entries in this dataframe suggests that it is also a personal decision by 
the winemaker himself. Adding this can impart a "fresh" feel to the wine's 
taste, though again, this is at the winemaker's discretion; not all good wines
require that "zing".    

> I was very surprised that residual sugar had almost zero correlation with wine
rating. Perhaps that is the point: I am not a wine-drinker, and I tend to 
enjoy sweeter drinks. Obviously, one's palate must be broadened in order to 
truly appreciate the subtleties of such a high-class beverage.

> Wine-tasting is a complex subject, and is itself subject to human biases. In 
that vein, perhaps it would have served the data well to include qualitative
or categorical variables to the list, instead of purely numerical ones. Things
like the color and hue of the wine might have contributed to rating as well. At
the end of the day, the linear model I constructed was too simple to adequately
explain wine rating. Wine is no doubt more than the sum of its parts, and 
certainly more than a few chemical components. 